Some forms of uncertainty may suppress the evolution of social learning

### 2022-04-20 ms.tex
small edits to new model parts

\subsection{Agents and learning}

In each time step, $N$ agents---autonomous problem solvers---select 
which behavior to perform based on their running tally of mean payoffs for 
each available behavior. %information (Figure~\ref{fig:behaviorSelection}). 
Agent $i$ tracks the mean payoff of each behavior $b$, denoted $\bar\pi_{ib}$, and
a \emph{count} of how many times it has performed each behavior, denoted $c_{ib}$.
$\bar\pi_{ib}$
is initialized to 0 for all $b$ at model initialization for
all agents, and after each generation for individual learner agents. Social
learning agents' $\bar\pi_{ib}$ is initialized as that of its teacher selected
through performance-biased oblique learning.

@@

\begin{table}[h]
    \caption{Dynamic agent-level variables.}
    \label{tab:modelParameters}
    \centering \hspace{-3em}
    \begin{tabular}{cp{4.0in}l} \toprule

@@

Social learning in this model is oblique, which here means
any agent from the previous generation, including an agent's parent,
could be an agent's teacher. 
Agents learn from exactly one teacher, selected as follows:
First, a learner agent from a new generation selects $N_T$ teachers at random.
The best-performing of the $N_T$ becomes a new agent's teacher, with ties broken
randomly. At the end of each generation, all agents die off with some selected
randomly for reproduction, weighted by accumulated payoffs within the round.

>>>>

\subsection{Agents and their attributes}

In each time step, $N$ agents---autonomous problem solvers---select 
which behavior to perform based on their running tally of mean payoffs for 
each available behavior. %information (Figure~\ref{fig:behaviorSelection}). 
Agent $i$ tracks the mean payoff of each behavior $b$, denoted $\bar\pi_{ib}$, and
a \emph{count} of how many times it has performed each behavior, denoted $c_{ib}$.
$\bar\pi_{ib}$
is initialized to 0 for all $b$ at model initialization for
all agents, and after each generation for individual learner agents. Social
learning agents' $\bar\pi_{ib}$ is initialized as that of its teacher selected
through performance-biased oblique learning. Agent $i$'s accumulated payoffs
from performing several behaviors over their lifetime of $M$ time steps is
denoted $\pi_{i}$.

@@

\begin{table}[h]
    \caption{Dynamic agent-level variables. Each has an implicit time dependence.}
    \label{tab:modelParameters}
    \centering \hspace{-3em}
    \begin{tabular}{cp{4.0in}l} \toprule

@@
